Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex

Twenty-six (26) participants responded, from which we selected the first 20, ten of which were female.  All participants spoke English, but 12 of them were non-native English speakers.  Seven were non-students, comprising University staff and alumni; out of the remaining 13, eight studied computer science and 5 studied other subjects.   On average, each study took 40 minutes to complete.  The information in Table \ref{tbl:data} summarises the metrics that were captured of the trials for each participant. We analyse this data next.

\begin{table*}[htbp]
\small
\begin{center}
\begin{tabular}{|r|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|}
\hline
Participants & 1 &2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20\\
\hline\hline
gender&f&m&f&f&f&f&f&m&f&f&m&f&m&f&m&m&m&m&m&m\\
A condition first task &y&y&y&n&n&y&n&n&y&y&n&n&y&y&n&n&n&n&n&n\\
\hline\hline
A Condition: task &4&2&3&4&3&&2&1&4&1&4&1&3&2&3&2&1&4&3&2\\
paper used&n&n&n&n&n&n&y&n&y&y&n&y&n&n&y&n&n&n&n&n\\
charts used &1&2&2&0&2&4&5&0&0&0&2&3&2&0&0&0&3&3&4&1\\
maps used &1&1&2&2&2&1&1&0&1&0&1&1&2&1&0&1&0&0&2&1\\ 
same as used &4&3&3&6&0&2&0&2&1&0&6&5&6&2&7&0&6&7&7&7\\
\# data sources used &4&3&4&4&4&3&4&3&4&4&3&3&5&4&5&4&4&5&5&4\\
chosen restaurant/uni &4.1&2.4&3.5&4.3&3.3&&2.4&1.4&4.2&1.6, \newline 1.3, \newline 1.2& 4.2& 1.4, \newline 1.5, \newline 1.3& 3.2& 2.1, \newline 2.3, \newline 2.6& 3.5, \newline 3.3&2.6, \newline 2.3, \newline 2.5&1.6, \newline 1.5, \newline 1.3&4.1&3.3&2.4, \newline 2.5, \newline 2.6\\
\# factors in choice &-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-\\
\hline\hline
 B Condition:task &3&&4&3&4&2&1&2&2&3&2&3&1&4&1&4&2&2&1&3\\
 paper used &n&n&n&n&n&n&y&n&y&y&n&y&n&y&y&n&n&y&n&n\\
 spreadsheet/website&&&&&&&&&&&&&&&&&&&&\\
 number of spreadsheets used&5/5&4/4&2/5&1.5&2/5&5/5&4/4&2/4&3/4&&2/4&4/5&2/4&4/5&2/4&2/5&4/4&4/4&0&5/5\\
 number of websites used&1&1&4&3&3&0&2&3&2&&1&2&3&1&2&3&2&0&4&0\\
 chosen restaurant/uni&3.5&&4.2&3.3&4.3&2.1&1.4, \newline 1.2, \newline 1.6&2.1&2.3, \newline 2.6, \newline 2.5&3.5&2.2, \newline 2.3, \newline 2.6&3.5&1.1&4.1&1.6&4.2&2.6, \newline 2.3, \newline 2.5&2.3, \newline 2.5, \newline 2.6&1.1, \newline 1.3,  \newline 1.4&3.5\\
 \# factors in choice &-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-\\
 \hline
\end{tabular}
\end{center}
\caption{Participants data.} \label{tbl:data}
\normalsize
\end{table*}

>>>>

We received 26 responses to our call for participants, from which we selected the first 20 (ten of which were female). Seven were non-students, comprised of university staff and alumni; the remainder were students, 8 studying computer science, and 5 studying other subjects.  On average, each study took 40 minutes to complete.  The information in Table \ref{tbl:data} summarises the captured metrics for each participant.

\begin{table*}[htbp]
\small
\begin{center}
\begin{tabular}{|r|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|p{0.3cm}|}
\hline
Participants & 1 &2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20\\
\hline\hline
gender&f&m&f&f&f&f&f&m&f&f&m&f&m&f&m&m&m&m&m&m\\
A condition first task &y&y&y&n&n&y&n&n&y&y&n&n&y&y&n&n&n&n&n&n\\
\hline\hline
A Condition: task &4&2&3&4&3&&2&1&4&1&4&1&3&2&3&2&1&4&3&2\\
paper used&n&n&n&n&n&n&y&n&y&y&n&y&n&n&y&n&n&n&n&n\\
charts used &1&2&2&0&2&4&5&0&0&0&2&3&2&0&0&0&3&3&4&1\\
maps used &1&1&2&2&2&1&1&0&1&0&1&1&2&1&0&1&0&0&2&1\\ 
same as used &4&3&3&6&0&2&0&2&1&0&6&5&6&2&7&0&6&7&7&7\\
\# data sources used &4&3&4&4&4&3&4&3&4&4&3&3&5&4&5&4&4&5&5&4\\
chosen restaurant/uni &4.1&2.4&3.5&4.3&3.3&&2.4&1.4&4.2&1.6, \newline 1.3, \newline 1.2& 4.2& 1.4, \newline 1.5, \newline 1.3& 3.2& 2.1, \newline 2.3, \newline 2.6& 3.5, \newline 3.3&2.6, \newline 2.3, \newline 2.5&1.6, \newline 1.5, \newline 1.3&4.1&3.3&2.4, \newline 2.5, \newline 2.6\\
\# factors in choice &-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-\\
\hline\hline
 B Condition:task &3&&4&3&4&2&1&2&2&3&2&3&1&4&1&4&2&2&1&3\\
 paper used &n&n&n&n&n&n&y&n&y&y&n&y&n&y&y&n&n&y&n&n\\
 spreadsheet/website&&&&&&&&&&&&&&&&&&&&\\
 number of spreadsheets used&5/5&4/4&2/5&1.5&2/5&5/5&4/4&2/4&3/4&&2/4&4/5&2/4&4/5&2/4&2/5&4/4&4/4&0&5/5\\
 number of websites used&1&1&4&3&3&0&2&3&2&&1&2&3&1&2&3&2&0&4&0\\
 chosen restaurant/uni&3.5&&4.2&3.3&4.3&2.1&1.4, \newline 1.2, \newline 1.6&2.1&2.3, \newline 2.6, \newline 2.5&3.5&2.2, \newline 2.3, \newline 2.6&3.5&1.1&4.1&1.6&4.2&2.6, \newline 2.3, \newline 2.5&2.3, \newline 2.5, \newline 2.6&1.1, \newline 1.3,  \newline 1.4&3.5\\
 \# factors in choice &-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-&-\\
 \hline
\end{tabular}
\end{center}
\caption{Data collected from each of our trials, for each participant.} \label{tbl:data}
\normalsize
\end{table*}
